Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2015-01-10 ch-tms/tms.tex
After first review in 2014

% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{cs_sfig1_all}
\caption[Schematic diagrams of tungsten power oxidization, seeded growth of \ce{WO3} NW, and sulfurization process.]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process. (d) Chemical vapor deposition system temperature profile measured at ambient condition. The zero inch location is defined at the upstream edge of furnace.}
\label{fig:ch5grow}
\end{figure}

@@

Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs. Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively. A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization. The measured layer spacing is 6.4 \si{\angstrom}, slight larger than bulk 2H-\ce{WS2} of 6.16 \si{\angstrom}, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}. The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.
% tem core shell layer
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
\caption{HRTEM imaging on one core-shell nanowire showing layer number changes.}
\label{fig:ch5ws2tem1}
\end{figure}
After examining dozens of core-shell NWs, it was found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification. Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW. The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2. Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending. \ce{WS2} fullerene also show similar structures. Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth3}
\caption{HRTEM imaging on the tip area of one core-shell nanowire.}
\label{fig:ch5ws2tem3}
\end{figure}
As illustrated in Fig.~\ref{fig:ch5ws2tem4}, complicated \ce{WS2} encapsulation was observed on one tapered core-shell NW. This tapering probably arose from the sulfurization process, but could be also due to the parent \ce{WO3} NW. The diameter varied from about 200 nm to 15 nm, and the \ce{WS2} layer number also changed in a nonlinear manner. On some turning region, the \ce{WS2} seems penetrating into the body of primary \ce{WO3} NW. 
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth4}
\caption{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers}
\label{fig:ch5ws2tem4}
\end{figure}

@@

No obviously consumed core region was observed among most of the core-shell NWs examined under TEM. An exception is shown in Fig.~\ref{fig:ch5ws2tem2}. It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model. 
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth1}
\caption{HRTEM imaging on one core-shell nanowire showing consumed core.}
\label{fig:ch5ws2tem2}
\end{figure}

@@

\Gls{pl} was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates. A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} is presented in Fig.~\ref{fig:ws2ramall}. This pattern was acquired on the middle spot of the core-shell NW shown as inset. Using 532 nm excitation, the multi-phonon resonant feature was clearly resolved. A broad PL peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.  
% ws2/wo3 on sio2,1 
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2_sio2_all}
\caption{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
\label{fig:ws2ramall}
\end{figure}
Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak. The origin of this peak family is still under research. A possible candidate points at the hydrocarbon contamination attached onto the core-shell NWs, as already been observed using TEM imaging. Interesting the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}. This comparison suggested there might be some enhancement mechanism from \ce{WS2} resonant Raman vibrations. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
\caption{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
\label{fig:ws2ramblue}
\end{figure}
Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm, with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}. The Raman patterns are shown in Fig.~\ref{fig:ws2ram3site}a-b. The off-resonance profile in Fig.~\ref{fig:ws2ram3site}b shows only two modes, with $E_{2g}^1$ mode at about 357 \si{cm^{-1}} and $A_{1g}$ mode at $418\sim419$ \si{cm^{-1}}. In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibits much richer spectra. The shoulder mode at tip2 spectrum is a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer. According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-walled \ce{WS2}. 
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:green}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_green}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
\caption{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
\label{fig:ws2ram3site}
\end{figure}
This predication is confirmed by the associated PL measurement as displayed in Fig.~\ref{fig:ws2plgreen}. Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2. The PL peaks centered at 1.958 and 1.934 eV for mid and tip1, respectively. The second and third order peaks also show up on all three Raman sites. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{core-shell-sio2-pl_green}
\caption[PL spectra of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si]{PL spectrum acquired on the core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
\label{fig:ws2plgreen}
\end{figure}

>>>>

% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{cs_sfig1_all}
\caption[Schematic diagrams of tungsten power oxidization, seeded growth of \ce{WO3} NW, and sulfurization process]{Schematic diagrams of (a) tungsten power oxidization, (b) seeded growth of \ce{WO3} NW, and (c) sulfurization process. (d) Chemical vapor deposition system temperature profile measured at ambient condition. The zero inch location is defined at the upstream edge of furnace.}
\label{fig:ch5grow}
\end{figure}

@@

Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs. Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively. A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization. The measured layer spacing is 6.4 \si{\angstrom}, slight larger than bulk 2H-\ce{WS2} of 6.16 \si{\angstrom}, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}. The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.
% tem core shell layer
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
\caption[HRTEM imaging on one core-shell nanowire showing layer number variation]{HRTEM imaging on one core-shell nanowire showing layer number variation.}
\label{fig:ch5ws2tem1}
\end{figure}
After examining dozens of core-shell NWs, it was found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification. Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW. The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2. Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending. \ce{WS2} fullerene also show similar structures. Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth3}
\caption[HRTEM imaging on the tip area of one core-shell nanowire]{HRTEM imaging on the tip area of one core-shell nanowire.}
\label{fig:ch5ws2tem3}
\end{figure}
As illustrated in Fig.~\ref{fig:ch5ws2tem4}, complicated \ce{WS2} encapsulation was observed on one tapered core-shell NW. This tapering probably arose from the sulfurization process, but could be also due to the parent \ce{WO3} NW. The diameter varied from about 200 nm to 15 nm, and the \ce{WS2} layer number also changed in a nonlinear manner. On some turning region, the \ce{WS2} seems penetrating into the body of primary \ce{WO3} NW. 
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth4}
\caption[HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers]{HRTEM imaging on one tapered core-shell nanowire showing fluctuation of layer numbers.}
\label{fig:ch5ws2tem4}
\end{figure}

@@

No obviously consumed core region was observed among most of the core-shell NWs examined under TEM. An exception is shown in Fig.~\ref{fig:ch5ws2tem2}. It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model. 
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth1}
\caption[HRTEM imaging on one core-shell nanowire showing consumed core]{HRTEM imaging on one core-shell nanowire showing consumed core.}
\label{fig:ch5ws2tem2}
\end{figure}

@@

\Gls{pl} was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates. A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} is presented in Fig.~\ref{fig:ws2ramall}. This pattern was acquired on the middle spot of the core-shell NW shown as inset. Using 532 nm excitation, the multi-phonon resonant feature was clearly resolved. A broad PL peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.  
% ws2/wo3 on sio2,1 
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2_sio2_all}
\caption[Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
\label{fig:ws2ramall}
\end{figure}
Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak. The origin of this peak family is still under research. A possible candidate points at the hydrocarbon contamination attached onto the core-shell NWs, as already been observed using TEM imaging. Interesting the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}. This comparison suggested there might be some enhancement mechanism from \ce{WS2} resonant Raman vibrations. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
\caption[Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
\label{fig:ws2ramblue}
\end{figure}
Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm, with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}. The Raman patterns are shown in Fig.~\ref{fig:ws2ram3site}a-b. The off-resonance profile in Fig.~\ref{fig:ws2ram3site}b shows only two modes, with $E_{2g}^1$ mode at about 357 \si{cm^{-1}} and $A_{1g}$ mode at $418\sim419$ \si{cm^{-1}}. In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibits much richer spectra. The shoulder mode at tip2 spectrum is a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer. According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-walled \ce{WS2}. 
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:green}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_green}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
\caption[Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
\label{fig:ws2ram3site}
\end{figure}
This predication is confirmed by the associated PL measurement as displayed in Fig.~\ref{fig:ws2plgreen}. Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2. The PL peaks centered at 1.958 and 1.934 eV for mid and tip1, respectively. The second and third order peaks also show up on all three Raman sites. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{core-shell-sio2-pl_green}
\caption[PL spectra of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si]{PL spectrum acquired on the core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
\label{fig:ws2plgreen}
\end{figure}

### 2015-01-10 ch-tms/tmspart.tex
camera ready
After first review in 2014

The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}.
\end{equation}
Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the cosine times 2 is unit. In analog with carbon nanotube, chiral angle $\theta$ is given by
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}.
\end{equation}
Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tubes. Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,\pi/6)$. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

@@

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{TMDC few layer growth methods summary}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2.5in}p{4.5in}}
\toprule
TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
\midrule
\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Zhan2012} & 1-5 nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30 min, 550-750@90 min and hold for 10 min. Mo coating on Si did not work.\\
\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4 nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3 min growth, atmospheric pressure, quick cooling\\

@@

% irreducible representation
\begin{table}[htb]
\centering
\caption[Lattices vibration of \ce{MS2}]{Lattices vibration of \ce{MS2}, reproduced from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
\begin{tabular}{lcccc}
\toprule
 $D_{6h}$   & $D_{3h}$ & Character &  Direction & Atoms  \\
\midrule
$A_{1g}$    &  $A_1^{'}$   & Raman     & (out of plane)  & S  \\
$E_{2g}^2$  &          &           & (in plane)      & M + S  \\
$E_{2g}^1$  &  $E'$    &           & (in plane)      & M + S  \\
$E_{1g}$    &  $E''$    &           & (in plane)      & S  \\
\midrule
$A_{2u}$    &  $A_2''$  & Infrared  & (out of plane)  & M + S  \\
$E_{1u}$    &          &           & (in plane)      & M + S  \\
\midrule
$A_{2u}$    &  $A_2^{''}$   & Acoustic  & (out of plane)  & M + S  \\
$E_{1u}$    &          &           &       &    \\
\midrule
$B_{2g}^2$  &          & Inactive  & (out of plane)  & M + S  \\
$B_{2g}^1$  &          &           & (out of plane)  & M + S  \\
$B_{1u}$    &          &           & (out of plane)  & S  \\
$E_{2u}$    &          &           & (in plane)      & S  \\
\bottomrule
\end{tabular}
\end{table}
The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations. $A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms. The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
each other and appears at very low frequencies ($<50$ \si{cm^{-1}} \cite{Zhang2013e}). The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration. In 2H-type TMDC, the $A_{1g}$ mode is more sensitive to electrostatic doping, while $E_{2g}^1$ mode is more sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}

>>>>

The geometrical symmetry groups of WS2 NT.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}.
\end{equation}
Notice $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where the $\cos\pi/3 \times 2 = 1$. In analog with carbon nanotube, chiral angle $\theta$ is given by
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}.
\end{equation}
Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tubes. Tubes $(n,0)$ with zero chiral angle are named zigzag, tubes $(n,n)$ with $\pi/6$ chiral angle are armchair, whereas all others are referred as chiral ones with $\theta \in (0,\pi/6)$. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

@@

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{Summary of TMDC few layer growth methods}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2.5in}p{4.5in}}
\toprule
TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
\midrule
\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Zhan2012} & 1-5 nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30 min, 550-750@90 min and hold for 10 min. Mo coating on Si did not work.\\
\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4 nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3 min growth, atmospheric pressure, quick cooling\\

@@

% irreducible representation
\begin{table}[htb]
\centering
\caption[Lattices vibration modes of \ce{MS2}]{Lattices vibration of \ce{MS2}, reproduced from Ref.\cite{Molina-Sanchez2011}}\label{tab:tmslattice}
\begin{tabular}{lcccc}
\toprule
 $D_{6h}$   & $D_{3h}$ & Character &  Direction & Atoms  \\
\midrule
$A_{1g}$    &  $A_1^{'}$   & Raman     & (out of plane)  & S  \\
$E_{2g}^2$  &          &           & (in plane)      & M + S  \\
$E_{2g}^1$  &  $E'$    &           & (in plane)      & M + S  \\
$E_{1g}$    &  $E''$    &           & (in plane)      & S  \\
\midrule
$A_{2u}$    &  $A_2''$  & Infrared  & (out of plane)  & M + S  \\
$E_{1u}$    &          &           & (in plane)      & M + S  \\
\midrule
$A_{2u}$    &  $A_2^{''}$   & Acoustic  & (out of plane)  & M + S  \\
$E_{1u}$    &          &           &       &    \\
\midrule
$B_{2g}^2$  &          & Inactive  & (out of plane)  & M + S  \\
$B_{2g}^1$  &          &           & (out of plane)  & M + S  \\
$B_{1u}$    &          &           & (out of plane)  & S  \\
$E_{2u}$    &          &           & (in plane)      & S  \\
\bottomrule
\end{tabular}
\end{table}
The $E$ type phonon branches correspond to in-plane normal modes, while the $A$ type phonons result from out-of-plane vibrations. $A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms. The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
each other and appears at very low frequencies ($<50$ \si{cm^{-1}} \cite{Zhang2013e}). The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration. In 2H-type TMDC, the $A_{1g}$ mode is more sensitive to electrostatic doping, while $E_{2g}^1$ mode is more sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.\cite{Zhao2013}
